SST_patterns

### 2019-11-02 SST_patterns.Rmd
updated
Update

# ANOVA
- Relationship between duration, year and distance as a function of the mean intensity.

```{r}
options(scipen = 999)
anova_func <- function(df){
  sites_aov <- aov(intensity_mean ~ site * duration * distance, data = df)
return(sites_aov)
}

@@

SACTN_anov <- sites_aov <- aov(intensity_mean ~ site * duration, data = SACTN_upwell_base)
summary(SACTN_anov)
```

@@

load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")

>>>>

# ANOVA
- Relationship between duration, year and site as a function of the distance

```{r}
options(scipen = 999)
anova_func <- function(df){
  sites_aov <- aov(distance ~ duration * site * site, data = df)
return(sites_aov)
}

@@

MUR_anov <- anova_func(df = MUR_upwell_base)
summary(MUR_anov)

SACTN_anov <- aov(intensity_mean ~ site * duration, data = SACTN_upwell_base)
summary(SACTN_anov)
```

@@

load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_upwell_base.RData")
